Types From Data: \textnormal{Making structured schema-free data formats first-class citizens in F\#}

### 2015-11-17 pldi-2016/paper.tex
Update paper.tex

In this case, the variant-annotated top type is ultimamtely presented as the following F\# type:
%
\begin{equation*}
\begin{array}{l}
 \kvd{type}~\ident{Element}~=  \\[0.1em]
 \quad \kvd{member}~\ident{Heading}~:~\ident{option}\langl \ident{string} \rangl\\
 \quad \kvd{member}~\ident{Paragraph}~:~\ident{option}\langl \ident{string} \rangl\\
 \quad \kvd{member}~\ident{Image}~:~\ident{option}\langl \ident{Image} \rangl\\
\end{array}
\end{equation*}
%
This still provides access to the possible elements known statically from the sample.
On the other hand, the user also needs to explicitly handle the casse when the value is none 
of the statically known elements. 
For example, the above code for  \strf{sample.doc} includes a \kvd{None -> ()} case to ensure that it will work 
correctly on a document containing elements not listed in the sample. Similarly, 
the program is not \emph{forced} to consider each of the possiblities in the annotations (in the manner
of complete-coverage checks for discriminated unions). For example,
the program is not forced to cover cases for  \ident{Paragraph} and \ident{Image}.  This is consistent
with our design principles, which prefer records (with optional properties) over discriminated unions.

>>>>

In this case, the variant-annotated top type is ultimately presented as the following F\# type:
%
\begin{equation*}
\begin{array}{l}
 \kvd{type}~\ident{Element}~=  \\[0.1em]
 \quad \kvd{member}~\ident{Heading}~:~\ident{option}\langl \ident{string} \rangl\\
 \quad \kvd{member}~\ident{Paragraph}~:~\ident{option}\langl \ident{string} \rangl\\
 \quad \kvd{member}~\ident{Image}~:~\ident{option}\langl \ident{Image} \rangl\\
\end{array}
\end{equation*}
%
This still provides access to the possible elements known statically from the sample.
The access is, however, deliberately weak, because the user needs to explicitly handle the casse when the value is none 
of the statically known elements. 
For example, the above code for  \strf{sample.doc} includes a \kvd{None -> ()} case to ensure that it will work 
correctly on a document containing elements not listed in the sample. Furthermore, 
the programmer is not \emph{forced} to consider each of the possiblities in the annotations. For example,
the program is not forced to include cases for  \ident{Paragraph} and \ident{Image}.  
Both of these weakenings are consistent with our design principles, 
which prefer records (with optional properties) over discriminated unions, in order to support 
open-world data and dot-driven developer tooling.
